%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[12pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{black}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
\renewcommand{\sfdefault}{lmss}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\renewcommand{\rmdefault}{ppl}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% Allows a command to be repeated.
\usepackage{expl3}
\ExplSyntaxOn
\cs_new_eq:NN \Repeat \prg_replicate:nn
\ExplSyntaxOff

\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.85]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{tikz}

% Put at the end!
\usepackage{anyfontsize}
\newenvironment{hidden}{\color{white}\fontsize{1}{1}\selectfont}{}


% personal data
\name{David}{Vaillant}
%\title{Resumé title}                               % optional, remove / comment the line if not wanted
% \address{San Jose, CA}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\phone[mobile]{(408)~439~7551}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
\email{david@vaillant.io}                               % optional, remove / comment the line if not wanted
%\homepage{vaillant.io}                         % optional, remove / comment the line if not wanted
%\social[linkedin]{john.doe}                        % optional, remove / comment the line if not wanted
%\social[twitter]{jdoe}                             % optional, remove / comment the line if not wanted
\social[github]{D-Vaillant}                              % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\newcommand{\tikzcircle}[2][color2,fill=color1]{\tikz[baseline=-0.5ex]\draw[#1,radius=#2] (0,0) circle ;}%
\newcommand{\progress}[1]{\Repeat{#1}{\tikzcircle{2.75pt}\,}\Repeat{5-#1}{\tikzcircle[color2,fill=white]{2.75pt}\,}}%
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Experience}
	\vspace{.5em}
	\cventry{2021--Present}{Support Technician}{X (via ERGInc)}{Mountain View}{}{%
        Managed customer fulfillment, organized and tracked device inventory, and worked with Data Science to provide useful insights to the rest of the team. 
		\begin{itemize}%
			\setlength\itemsep{.2em}
			\item Further developed nascent inventory management system, greatly decreasing the amount of taken to batch edit device states and creating a SQL interface.
            \item Created ETL pipelines between our inventory management system, existing device information, and Salesforce.
            \item Worked with hardware team to design and run temperature validation processes. Transitioned process from manual work done via Mathematica to an automated Python script that uploads results directly to a BigQuery database.
        \end{itemize}}
		\vspace{.5em}

	\cventry{2019--2021}{Software Quality Specialist}{Waymo (via Crowdstaffing)}{Mountain View}{}{%
        Analyzed instances of misbehavior by self-driving vehicles and applied root cause analysis to determine the specific software system responsible.
		\begin{itemize}%
			\setlength\itemsep{.2em}
			\item Streamlined the software fault analysis workflow using SQL-driven dashboards.
			\item Implemented productivity-saving features for proprietary applications.
			\item Designed and managed the rollout of new workflows across multiple teams.
		\end{itemize}}
		\vspace{.5em}

	\cventry{2017--2018}{Mathematics Tutor}{West Valley College}{Saratoga}{}{%
        Tutored disadvantaged students in algebra, statistics, and fundamental concepts in mathematics.}
		\vspace{.5em}

	\cventry{2015--2016}{Technical Intern}{Desert Farms Camel Milk}{Santa Monica}{}{%
        Provided technical support for an online small business. 
		\begin{itemize}%
			\setlength\itemsep{.2em}
			\item Saved hours of manual labor by programmatically querying and organizing customer orders using Ruby scripting.
			\item Improved the performance and responsivity of the online storefront, increasing customer satisfaction and retention.
		\end{itemize}}

\section{Education}
\vspace{.5em}

\cventry{2010--2014}{BSc. Mathematics}{University of California, Santa Barbara}{}{}{Studied combinatorics, graph theory, linear algebra, and the foundations of statistics.}  % arguments 3 to 6 can be left empty

\cventry{}{BA. Philosophy}{}{}{}{Specialization in logic and the philosophy of mathematics.}  % arguments 3 to 6 can be left empty
%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}

\section{Proficiencies}
	\cvitem{\textbf{OS}}{Windows, Linux, FreeBSD}
    \cvitem{\textbf{Languages}}{Python, SQL, \LaTeX, C++}
    \cvitem{\textbf{Tools}}{bash, git, GCP (Cloud Run, Composer, BigQuery, Spanner), Salesforce}
\closesection

\begin{hidden}
	tensorflow keras scikit-learn machine learning statistical techniques models business effective project planning complex r sas python hadoops wide variety tools languages collaboration team decisions predictive data innovates effective communication team player professional sqlite mysql sql postgresql nginx apache web javascript self driven starter innovative analytical spss scalable pipelines scraping scrapping non-linear linear regression modelling java html css

\end{hidden}

\end{document}
%\clearpage

%% end of file `template.tex'.
